Learning CNN filters from user-drawn image markers for coconut-tree image classification

### 2020-07-23 main.tex
change projection image in pipeline figure
pipeline add markers

\usepackage{tikz}
\usetikzlibrary{calc}
\usetikzlibrary{shapes.geometric, arrows, fit}
\usepackage{varwidth}
\usetikzlibrary{positioning}
\usetikzlibrary{backgrounds}

@@

@@

     \node (vis1) [image, right=1.5em of tsne, outer sep=-15pt] {\includegraphics[width=.15\textwidth]{figures/input.png}};

@@

>>>>

\usepackage{tikz}
\usetikzlibrary{calc}
\usetikzlibrary{shapes.geometric, arrows, fit}
\usepackage{varwidth}
\usetikzlibrary{positioning}
\usetikzlibrary{backgrounds}
\usetikzlibrary{decorations.pathreplacing}

@@

    \tikzstyle{steps} = [rectangle, rounded corners, minimum width=1.3cm, minimum height=0.5cm,text centered, draw=pink, thick, fill=heliotrope!30, execute at begin node={\begin{varwidth}{2.5cm}},
    execute at end node={\end{varwidth}}]
    \tikzstyle{image} = [minimum width=1.3cm, minimum height=0.7cm,text centered, draw=white,fill=white!30, inner sep=0pt]

     \node (imgs) [fit={($(img1.north west)+(-0.45,0.1)$) ($(img3.south east)+(0.45,-0.1)$)}, inner sep=0pt, draw=none, rounded corners, very thick, label = {[label distance = 0.1em]below:{Training set}}] {};
     %----------------------------------

     \node (vis1) [image, right=1.5em of tsne, outer sep=0pt, label = {[label distance = 0.1em]below:{Projection}}] {\includegraphics[width=.12\textwidth]{figures/input_200.png}};

     \node (select) [steps, right=1.35em of vis1] {Select\\ Images};

    %images----------------------------
    \node (simg1) [image, above right=-2.5em and 3em of select] {\includegraphics[width=.08\textwidth]{figures/img1.png}};
    \node (simg2) [image, below left=-5em of simg1] {\includegraphics[width=.08\textwidth]{figures/img2.png}};
    \node (simg3) [image, below left=-5em of simg2] {\includegraphics[width=.08\textwidth]{figures/img3.png}};
    \node (simg4) [image, below left=-5em of simg3] {\includegraphics[width=.08\textwidth]{figures/img4.png}};

    \node (simgs) [fit={($(simg1.north west)+(-0.64,0.2)$) ($(simg4.south east)+(0.64,-0.2)$)}, inner sep=0pt, draw=none, label = {[label distance = 0.0em]above:{Selected images}}] {};
    %----------------------------------

     \node (put) [steps, right=1em of simgs] {Select\\Markers};

     %images----------------------------
    \node (mimg1) [image, above right=-2em and 2.8em of put] {\includegraphics[width=.08\textwidth]{figures/markers1.png}};
    \node (mimg2) [image, below left=-5em of mimg1] {\includegraphics[width=.08\textwidth]{figures/markers2.png}};
    \node (mimg3) [image, below left=-5em of mimg2] {\includegraphics[width=.08\textwidth]{figures/markers3.png}};
    \node (mimg4) [image, below left=-5em of mimg3] {\includegraphics[width=.08\textwidth]{figures/markers4.png}};

    \node (mimgs) [fit={($(mimg1.north west)+(-0.64,0.2)$) ($(mimg4.south east)+(0.64,-0.2)$)}, inner sep=0pt, draw=none, label = {[label distance = 0.0em]above:{Markers}}] {};

    \node (flim) [steps, right=1em of mimgs] {FLIM};

    \node (ft) [steps, below=5em of flim] {Feature\\Extractor};

    \node (user) [image, below=2em of simgs, outer sep = -.5em] {\includegraphics[width=.07\textwidth]{figures/user.png}};

     %--------------------------------------------------------------arrows
     \draw [arrow, myarrow] (imgs) -- (tsne);
     \draw [arrow, myarrow] (tsne) -- (vis1);
     \draw [arrow, myarrow] (vis1) -- (select);
     \draw [arrow, myarrow] (select) -- (simgs);
     \draw [arrow, myarrow] (simgs) -- (put);
     \draw [arrow, myarrow] (put) -- (mimgs);
     \draw [arrow, myarrow] (mimgs) -- (flim);
     \draw [arrow, myarrow] (flim) -- (ft);
     \draw [arrow, myarrow] (user) -- (select);
     \draw [arrow, myarrow] (user) -- (put);

     %\draw [decorate,decoration={brace,amplitude=10pt,raise=4pt},yshift=0pt]
%(img3.west) -- (img1.north) node [black,midway,xshift=0.8cm, label = {[label distance = 0.1em]above:{Images}}] {};

\begin{comment}

@@

     \node (vis1) [image, right=1.5em of tsne, outer sep=0pt] {\includegraphics[width=.12\textwidth]{figures/input_200.png}};

@@

    \end{tikzpicture}
  \end{center}
  \caption{Pipeline.}
  \label{fig:pipeline}
\end{figure*}
\end{comment}
